A Survey of Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
minor wording changes

Wearables are the new frontier of ubiquitous computing, with new capabilities can capture unique data about the user and his/her surroundings. As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security~\cite{palen2003unpacking}. Privacy in ubiquitous systems can be achieved by adhering to principles such as notice, choice, and consent~\cite{langheinrich2001privacy}. An example of research which helps such principles include work by Egelman \etal , which evaluates various indicator designs to better communicate data capture on ubiquitous computing platforms.

>>>>

Wearables are the new frontier of ubiquitous computing, with new capabilities can capture unique data about the user and his/her surroundings. As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security~\cite{palen2003unpacking}. Privacy in ubiquitous systems can be achieved by adhering to principles such as notice, choice, and consent~\cite{langheinrich2001privacy}. An example of research which aims to uphold such principles include work by Egelman \etal , which evaluates various indicator designs to better communicate data capture on ubiquitous computing platforms.
